### 2013-08-14 pystruct/paper.tex
Moving around a lot of sections, renaming conclusion to summary, starting to merge mil and semisupervised, starting to rework structur of pystruct and exact learning.

@@

@@

\section{Structured Prediction and Casting it into Software}\label{sec:api}

@@

@@

Estimating $\theta$ is done in \texttt{learner} classes, which currently support
cutting plane algorithms for structural support vector machines~(SSVMs), subgradient methods for SSVMs,
the structured perceptron and latent variable SSVMs. The cutting plane implementation uses the {\sc cvxopt} package \citep{dahl2006cvxopt}
for quadratic optimization.
Encoding the structure of the problem is done using \texttt{model} classes, which
compute $\Psi$ and encode the structure of the problem.
\pystruct implements models for many common cases, such as multi-class and
multi-label classification, conditional random fields with constant or
data-dependent pairwise potentials, and several latent variable models.
The maximization for finding $y$ in Equation~\ref{eq:main_equation} is carried out
using highly optimized implementations from external libraries. \pystruct
includes support for using {\sc OpenGM}~\citep{kappes2013comparative}, {\sc
LibDAI}~\citep{Mooij_libDAI_10}, QPBO fusion moves~\citep{rother2007optimizing},
and {\sc AD$^3$}~\citep{martins2011augmented}. It also includes an interface to
a general purpose linear programming solver from \textsc{cvxopt}~\cite{dahl2006cvxopt}.

@@

\section{Usage Example: Semantic Image Segmentation}\label{sec:examples}
%\subsection{Multi-class classification}
%Multi-class classification is a very simple case of structured prediction, that serves
%well to exemplify the usage. We load the iris dataset and compare the usage of \pystruct
%with a call to LibLinears Crammer-Singer SVM using scikit-learn.
%\lstinputlisting[language=Python, frame=single, basicstyle=\scriptsize,
    %numbers=left, commentstyle=\color{blue}\normalfont,
%columns=flexible, firstline=11]{multi_class_example.py}
%\subsection{OCR sequence classification}
%Chain structured CRFs are commonly used in natural language processif, for
%example for part-of-speech tagging or named entity recognition.  Here we
%demonstrate the use of a chain CRF on the OCR dataset from. The ChainCRF provides
%a very simnple interface for this problem. Each example is presented as an
%array of input features of shape % (length_of_sequence, number_of_features).
%% listing, training time, accuracy, comparision with kraehenbuehl

@@

\section{Conclusion}
This paper introduced \pystruct, a modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations.
\pystruct integrates itself into the scientific Python eco-system, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches. In the future,
we plan to integrate other paradigms, such as sampling-based learning~\citep{wick2011samplerank},
surrogate objectives (for example pseudo-likelihood), and approaches that allow for a better integration
of inference and learning~\citep{meshi2010learning}.

>>>>

Many classical computer vision applications such as stereo, optical flow, semantic
segmentation and visual grouping can be naturally formulated as image labeling tasks.

Arguably the most popular way to approach such labeling problems is via graphical
models, such as Markov random fields (MRFs) and conditional random fields (CRFs).
MRFs and CRFs provide a principled way of integrating local evidence and
modeling spacial dependencies, which are strong in most image-based tasks.

While in earlier approaches, model parameters were set by hand or using
cross-validation, more recently parameters are often learned using a max-margin
approach.

Most models employ linear energy functions of unary and pairwise interactions,
trained using structural support vector machines (SSVMs). While linear energy
functions lead to learning problems that are convex in the parameters, complex
constraints complicate their optimization.

@@

In this chapter, we will first introduce the concepts and algorithms used in structured prediction,
in particular in maximum margin methods. We will then accompany this by a description of our
open source implementation of these algorithms, \pystruct.

@@

\section{Basic Concepts in Structured Prediction}

@@

% TODO relate to computer vision here
When learning for structured prediction in the max-margin framework of
\cite{tsochantaridis2006large}, predictions are made as
\[ \argmax_y f(x, y, \theta)\]
where x is the input and $\theta$ are the parameters to be learned.
Here, $f$ is a compatibility function of $x$ and $y$, that is linear in the parameters
\[f(x, y, \theta) = \langle \theta, \Psi(x, y) \rangle\]
where $\Psi(x, y)$ is a joint feature vector of $x$ and $y$. Specifying a specific CRF model
amounts to specifying $\Psi$.

For a given loss $\Delta$, the parameters $\theta$ are learned by minimizing
the loss base soft-margin objective
\begin{equation}\label{mainequation}
    \min_\theta \frac{1}{2} ||\theta||^2 + C \sum_i  r_i(\theta)
\end{equation}
with regularization parameter $C$, where $r_i$ is an hinge-loss like upper
bound on $\Delta$ empirical risk:
\[r_i(x_i, y_i, y) = [\max_{y \in \mathcal{Y}} \Delta(y_i, y) + \left<\theta, \psi(x_i, y) - \psi(x_i, y_i) \right >]_+ \]
\citep{ratliff2007online} derive convergence rates for a stochastic version of the subgradient of  Equation~\ref{mainequation}:
\begin{equation}\label{subgradient}
    g := \psi(x_i, y) - \psi(x_i, y_i) + \theta / C
\end{equation}
leading to a simple iterative optimization.

\section{Learning Algorithms for Linear Max-Margin Structured Prediction}
% TODO algorithms here
\subsection{The Cutting Plane Method}\label{cutting_plane}

When learning for structured prediction in the max-margin framework of
\citet{tsochantaridis2006large}, predictions are made as
\[ \argmax_{y \in \mathcal{Y}} f(x, y, \theta),\]
where $x \in \mathcal{X}$ is the input, $y \in \mathcal{Y}$ the prediction, and $\theta$ are the parameters to be learned.
We will assume $y$ to be multivariate, $y=(y_1, \dots, y_k)$ with possibly varying $k$.

The function $f$ measures compatibility of $x$ and $y$ and is a linear function of the parameters $\theta$:
\[f(x, y, \theta) = \langle \theta, \psi(x, y) \rangle.\]
Here $\psi(x, y)$ is a joint feature vector of $x$ and $y$. Specifying a particular SSVM model
amounts to specifying $\psi$.

For a given loss $\Delta$, the parameters $\theta$ are learned by minimizing
the loss-based soft-margin objective
\begin{equation}\label{eq:mainequation}
\min_\theta \frac{1}{2} ||\theta||^2 + C \sum_i  r_i(\theta)
\end{equation}
with regularization parameter $C$, where $r_i$ is a hinge-loss-like upper
bound on the empirical $\Delta$-risk:
\[r_i(x^i, y^i, y) = \left [\max_{y \in \mathcal{Y}} \Delta(y^i, y) + \left<\theta, \psi(x^i, y) - \psi(x^i, y^i) \right > \right]_+ \]

We solve the following reformulation of Equation~\eqref{mainequation}, known as one-slack QP formulation:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i,
            \hat{y}^i)] \right \rangle \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
using the cutting plane method described in
Algorithm~\ref{alg_cutting_plane}~\citep{joachims2009cutting}.

The cutting plane method alternates between solving Equation~\eqref{oneslack}
with a working set $\W$ of constraints, and expanding the working set using the
current $\theta$ by finding $\mathbf{y}$ corresponding to the most violated constraint,
using a separation oracle $I$.
We investigate the construction of $\W$ and the influence of $I$
on learning.

%TODO unstructured!!

Intuitively, the one-slack formulation corresponds to joining all training
samples into a single training example $(\mathbf{x}, \mathbf{y})$ that has no
interactions between variables corresponding to different data points.
Consequently, only a single constraint is added in each iteration of
Algorithm~\ref{alg_cutting_plane}, leading to very small $\W$. We further use
pruning of unused constraints, as suggested by \citet{joachims2009cutting},
resulting in the size of $\W$ being in the order of hundreds for all experiments.

We also use another enhancement of the cutting plane algorithm introduced by
\citet{joachims2009cutting}, the caching oracle. For each training example $(x^i, y^i)$,
we maintain a set $C^i$ of the last $r$ results of loss-augmented inference
(line~\ref{get_cutting_plane} in Algorithm~\ref{alg_cutting_plane}).
For generating a new constraint $(\hat{y}^1, \dotsc, \hat{y}^n)$ we find
\[ 
    \hat{y}^i \leftarrow \argmax_{\hat{y}\in C^i} \sum_{i=1}^n \Delta(y^i, \hat{y}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i, \hat{y})] \right \rangle
\]
by enumeration of $C^i$ and continue until line~\ref{convergence_check}.
Only if $\xi' - \xi < \epsilon$, i.e.\ the produced constraint is not violated, we
return to line~\ref{get_cutting_plane} and actually invoke the separation
oracle $I$.

In computer vision applications, or more generally in graph labeling problems,
$\psi$ is often given as a factor graph over $y$, typically using only unary and pairwise functions:
\[ \langle \theta, \psi(x, y) \rangle = \sum_{i=0}^k \langle \theta_u,  \psi_u(x, y_k) \rangle + \sum_{(i, j) \in E} \langle \theta_p, \psi_p(x, y_k, y_l) \rangle, \]
where $E$ a set of pairwise relations. In this form, parameters $\theta_u$ and $\theta_p$ for unary and
pairwise terms are shared across all entries and pairs.
The decomposition of $\psi$ into only unary and pairwise interactions allows
for efficient inference schemes, based on message passing or graph cuts.

\section{Casting Structured Prediction into Software}\label{sec:api}

@@

Estimating $\theta$ is done in \texttt{learner} classes, which currently
support cutting plane algorithms for structural support vector
machines~(SSVMs), subgradient methods for SSVMs, the structured perceptron and
latent variable SSVMs. The cutting plane implementation uses the {\sc cvxopt}
package \citep{dahl2006cvxopt} for quadratic optimization.

Encoding the structure of the problem is done using \texttt{model} classes, which
compute $\Psi$ and encode the structure of the problem.
\pystruct implements models for many common cases, such as multi-class and
multi-label classification, conditional random fields with constant or
data-dependent pairwise potentials, and several latent variable models.
The maximization for finding $y$ in Equation~\ref{eq:main_equation} is carried out
using highly optimized implementations from external libraries. \pystruct
includes support for using {\sc OpenGM}~\citep{kappes2013comparative}, {\sc
LibDAI}~\citep{Mooij_libDAI_10}, QPBO fusion moves~\citep{rother2007optimizing},
and {\sc AD$^3$}~\citep{martins2011augmented}. It also includes an interface to
a general purpose linear programming solver from \textsc{cvxopt}~\cite{dahl2006cvxopt}.

@@

\section{Usage Example: Semantic Image Segmentation}\label{sec:examples}
%TODO Multi-label, chain?

%\subsection{Multi-class classification}
%Multi-class classification is a very simple case of structured prediction, that serves
%well to exemplify the usage. We load the iris dataset and compare the usage of \pystruct
%with a call to LibLinears Crammer-Singer SVM using scikit-learn.
%\lstinputlisting[language=Python, frame=single, basicstyle=\scriptsize,
    %numbers=left, commentstyle=\color{blue}\normalfont,
%columns=flexible, firstline=11]{multi_class_example.py}
%\subsection{OCR sequence classification}
%Chain structured CRFs are commonly used in natural language processif, for
%example for part-of-speech tagging or named entity recognition.  Here we
%demonstrate the use of a chain CRF on the OCR dataset from. The ChainCRF provides
%a very simnple interface for this problem. Each example is presented as an
%array of input features of shape % (length_of_sequence, number_of_features).
%% listing, training time, accuracy, comparision with kraehenbuehl

@@

\section{Summary}
%TODO summarize structured prediction
This paper introduced \pystruct, a modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations.
\pystruct integrates itself into the scientific Python eco-system, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches. In the future,
we plan to integrate other paradigms, such as sampling-based learning~\citep{wick2011samplerank},
surrogate objectives (for example pseudo-likelihood), and approaches that allow for a better integration
of inference and learning~\citep{meshi2010learning}.
